% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[11pt,a4paper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{xcolor}

\newcommand{\updateinfo}[1][\today]{\par\vfill\hfill{\scriptsize\color{gray}Last updated on #1}}


\usepackage{fancyhdr}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage[none]{hyphenat}

% Set your name here
\def\name{Sandeep Rath}



\fancyhf{}
\cfoot{ Last updated: \today }
% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
%\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\name},
	pdfkeywords = {economics, statistics, mathematics},
	pdftitle = {\name: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\geometry{
	body={6.5in,10in},
	left=1.0in,
	top=1in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
	\begin{list}{}{
			\setlength{\leftmargin}{1.5em}
		}
	}{
\end{list}
}

\begin{document}

	% Place name at left
	{\huge \name}

	% Alternatively, print name centered and bold:
	%\centerline{\huge \bf \name}

	\vspace{0.25in}

	\begin{minipage}{0.45\linewidth}
		\href{http://www.unc.edu/}{
			Kenan Flagler Business School\\
			University of North Carolina} \\
		McColl 4705 \\
		CB\# 3490 \\
		Chapel Hill, NC 27599
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\begin{tabular}{ll}
			Phone: & (919) 962-3818 \\
			Fax: &  (919) 962-6949 \\
			Email: & \href{mailto:sandeep@unc.edu}{\tt sandeep@unc.edu} \\
			Homepage: & \href{https://rathsandeep.github.io/}{\tt rathsandeep.github.io}\\
		\end{tabular}
	\end{minipage}


	%\section*{Personal}

	%\begin{itemize}
	%\item Born on September 29, 1895.
	%\item United States Citizen.
	%\end{itemize}


	\section*{\textbf{Education}}

	\begin{itemize}
		\item \textbf{UCLA Anderson School of Management, Los Angeles}
		\begin{itemize}
			\item Ph.D. Management,  June, 2016.
			\item \emph{Dissertation Title}: Resource Planning Models for Healthcare Organizations.
			\item \emph{Dissertation committee}: Kumar Rajaram (chair), Felipe Caro, Uday Karmarkar, {Aman Mahajan}.
		\end{itemize}
		\item \textbf{Indian Institute of Technology, Kharagpur}
		\begin{itemize}
			\item M.Tech. Instrumentation Engineering, 2006.
			\item B.Tech. Electrical Engineering, 2006.
			\item Minor, Electronics and Telecommunication Engineering.
		\end{itemize}




	\end{itemize}


	\section*{\textbf{Professional Experience}}

	\begin{itemize}
		\item \textbf{Kenan-Flagler Business School, University of North Carolina at Chapel Hill}

		\begin{itemize}
			\item Assistant Professor, 2016--present.
		\end{itemize}
		\item \textbf{UCLA Anderson School of Management, Los Angeles}

		\begin{itemize}
			\item Teaching Assistant, Fall Quarters of 2012--2016.
		\end{itemize}

		\item \textbf{Indian School of Business, Hyderabad}

		\begin{itemize}
			\item Research Associate, 2010--2011.
		\end{itemize}


		\item \textbf{Schlumberger Ltd., Pune}
		\begin{itemize}
			\item Business Analyst,  2008--2009
			\item Manufacturing Engineer, 2007--2008.
		\end{itemize}
		\item \textbf{ITC Ltd., Chennai}

		\begin{itemize}
			\item Assistant Under Training, 2006--2007.
		\end{itemize}

	\end{itemize}

	\section*{\textbf{Honors}}

	\begin{itemize}
		\item UCLA Dissertation Year Fellowship, 2015--2016.
		\item UCLA Anderson Doctoral Fellowship, 2011--2015.
		\item Fellowship for Post Graduate Studies, Government of India,  2005--2006.
		\item National Talent Search Examination Scholarship, Government of India, 1999--2005.
	\end{itemize}


	\section*{\textbf{Publications}}

	\subsection*{Peer-Reviewed Journal Articles}

	\begin{itemize}
		\item Wood, B. C., Konchan, S., Gay, \textbf{S., Rath}, S., Deshpande, V., \& Knowles, M. (2021). Data Analysis of Plastic Surgery Instrument Trays Yields Significant Cost Savings and Efficiency Gains. \emph{Annals of Plastic Surgery}, 86(6S), S635-S639. (5 pages)
		\item Knowles, M., Gay, S.S., Konchan, S.K., Mendes, R., \textbf{Rath, S.}, Deshpande, V., Farber, M.A. and Wood, B.C., (2020). Data Analysis of Vascular Surgery Instrument Trays Yields Large Cost and Efficiency Savings. \emph{Journal of Vascular Surgery}, 71(1), pp.e15-e16 (10 pages).
		\item \textbf{Rath, S.}, Rajaram, K., \& Mahajan, A. (2017). Integrated Anesthesiologist and Room Scheduling for Surgeries: Methodology and Application. \emph{Operations Research}, 65(6), 1460-1478. \mbox{(18 pages)}.
		\item Deo, S., Rajaram, K., \textbf{Rath, S.}, Karmarkar, U. S., \& Goetz, M. B. (2015). Planning for HIV Screening, Testing, and Care at the Veterans Health Administration. \emph{Operations Research}, 63(2), 287-304 (18 pages).
	\end{itemize}
\subsection*{Non Peer-Reviewed Articles}

\begin{itemize}
	\item Rajaram, K., \& \textbf{Rath, S.} (2017). Managing the Operating Room Suite at UCLA Ronald Reagan Medical Center. \emph{Impact}, 3(2), 31-35.
\end{itemize}
\subsection*{Articles Under Review}
\begin{itemize}
	\item Deshpande V., Mundru N., \textbf{Rath, S.}, Knowles M., Rowe D., Wood B.C.,  Data-Driven Surgical Tray Optimization to Improve Operating Room Efficiency \emph{Under Review at Operations Research} (35 pages)
	\item \textbf{Rath, S.} and Rajaram, K.,  Staff Planning for Hospitals with Cost Estimation and
	Optimization \emph{Under  review at Production \& Operations  Management} (31 pages).
\end{itemize}

\subsection*{Working Paper}
\begin{itemize}
	\item \textbf{Rath, S.}, Swaminathan, J.M., Coleman C., Collaborative Care for Mental and Physical Health \emph{Preparing to submit to Operations Research} (34 pages)

\end{itemize}

\subsection*{Work in Progress}

\begin{itemize}

	\item Celik U., Kesavan S.,  \textbf{Rath, S.}, Staats B., Operational Impact of Physician Electronic Health Record Use
\end{itemize}

%	\subsection*{Other Published Articles}
%
%	\begin{itemize}
%		\item Rajaram, K., \& \textbf{Rath, S.} (2017). Managing the Operating Room Suite at UCLA Ronald Reagan Medical Center. Impact, 3(2), 31-35.
%	\end{itemize}


	\section*{\textbf{Teaching Record}}

	\begin{itemize}
		\item\textbf{ BSBA Program, Kenan-Flagler Business School, University of North
			Carolina}
		\begin{itemize}
			\item BUSI 403: Operations Management, Undergraduate Core, \emph{Spring 2017-2021 }

%			\begin{itemize}
%%				\item \emph{Spring 2019}: In progress
%%				\item \emph{Spring 2018}: Instructor Rating 4.58/5, 4.71/5
%%				\item \emph{Spring 2017}: Instructor Rating 4.79/5, 4.69/5
%
%			\end{itemize}


			\item BUSI 532H: Service Operations, Undergraduate Elective, \emph{Spring 2018-2021}
%			\begin{itemize}
%				\item \emph{Spring 2019}: In progress
%				\item \emph{Spring 2018}: Instructor Rating 4.82/5
%			\end{itemize}
		\end{itemize}

	\end{itemize}





	\section*{\textbf{Peer-Reviewed Conference Presentations}}
	\begin{itemize}

		\item \emph{Collaborative Care for Mental and Physical Health}
			\begin{itemize}
			\item Manufacturing \& Service Operations Management Conference, 2021.
		\end{itemize}
		\item \emph{Staff Planning for Hospitals with Cost Estimation and
			Optimization}
		\begin{itemize}
			\item Manufacturing \& Service Operations Management Conference, 2019.
			\item Manufacturing \& Service Operations Management Conference, 2018.

		\end{itemize}
	\end{itemize}
	\section*{\textbf{Invited Conference Presentations}}
	\begin{itemize}
		\item \emph{Appointment Scheduling with Off-line Discretionary Work}
		\begin{itemize}
			\item INFORMS Annual Meeting, Anaheim 2021 (\emph{scheduled}).
		\end{itemize}
		\item \emph{Collaborative Care for Mental and Physical Health}
		\begin{itemize}
			\item POMS, Online, 2021
			\item INFORMS Annual Meeting, Seattle, 2019.
			\item INFORMS Healthcare, Boston, 2019.
			\item INFORMS Annual Meeting, Phoenix 2018.
		\end{itemize}
		\item \emph{Staff Planning For Anesthesiologists}
		\begin{itemize}
			%\item INFORMS Annual Meeting, Phoenix 2018 (presented by co-author).
			\item INFORMS Annual Meeting, Seattle, 2019.
			\item INFORMS Healthcare, Boston, 2019.
			\item INFORMS Annual Meeting, Houston, 2017.
			\item  INFORMS Annual Meeting, Nashville, 2016.
		\end{itemize}
		\item \emph{Integrated Staff and Room Scheduling for Surgeries}
		\begin{itemize}
			\item INFORMS Healthcare, Rotterdam, 2017.
			\item INFORMS Annual Meeting, Nashville, 2016.
			\item INFORMS Annual Meeting, Philadelphia, 2015.
			\item INFORMS Healthcare, Nashville, 2015.
		\end{itemize}
		\item \emph{Planning for HIV Screening, Testing, and Care}
		\begin{itemize}
			\item INFORMS Annual Meeting, San Francisco, 2014.
		\end{itemize}
	\end{itemize}
	\section*{\textbf{Other Invited Presentations}}


	\begin{itemize}
		\item \emph{Collaborative Care for Mental and Physical Health}

		\begin{itemize}
			\item Consortium Friday Seminar Series by Indiana University (online), 2021
			\item UNC Business of Healthcare Convocation, Chapel Hill, 2019
		\end{itemize}

		\item\emph{ Integrated Staff and Room Scheduling for Surgeries}
		\begin{itemize}
			\item Kenan-Flagler Business School, University of North Carolina, Chapel-Hill, 2015.
			\item Communication, Networks and Systems Seminar, University of Southern California, 2015.
			\item Southern California OR/OM Day, Los Angeles, 2015.
		\end{itemize}
		\item \emph{Planning for HIV Screening, Testing and Care}
		\begin{itemize}
			\item DOTM Colloquium Series, UCLA Anderson, 2015.
		\end{itemize}
	\end{itemize}



	\section*{\textbf{Professional Service}}
	\subsection*{To the Discipline}
	\begin{itemize}
		\item \textbf{Reviewer}
		\begin{itemize}

			\item California Management Review, IISE Transactions,  Management Science, Manufacturing \& Service Operations Management, Naval Research Logistics, Operations Research, Production and Operations Management %(h-index: 209), Number of papers reviewed: 1


		\end{itemize}
		\item \textbf{Judge}
		\begin{itemize}
			\item MSOM Conference Healthcare SIG, 2021
			\item Pierskalla Best Paper Award, 2020
			\item POMS College of Healthcare Operations Management, Best Paper Competition, 2017, 2020, 2021.
		\end{itemize}
		\item \textbf{Conference Session Chair}
		\begin{itemize}
			\item INFORMS Annual Meetings: Anaheim (2021, \emph{scheduled}), Seattle (2019), Phoenix (2018, co-chair with Jayashankar  Swaminathan), Houston (2017), Philadelphia (2015)
			\item INFORMS Healthcare: Boston (2019), Nashville (2015)
			\end{itemize}

	\end{itemize}
	\subsection*{Within UNC Chapel Hill}
	\begin{itemize}
		\item Organizing Committee Member, UNC Healthcare Operations Workshop, 2019
		\item Operations Area Faculty Seminar Series, Chair, 2017-2019.
		\item Organizing Committee Member, Manufacturing \& Service Operations Management Conference, 2017.
	\end{itemize}
%	\section*{Memberships}
%	\begin{itemize}
%		\item Member, Institute for Operations Research and Management Science (INFORMS), 2012--present.
%	\end{itemize}
	% Footer
	\updateinfo[\today]

\end{document}
